---
title: "mini-project3"
author: "Peter Gao"
editor_options: 
  chunk_output_type: console
---

```{r}
library(ggplot2)
library(dplyr)
library(readr)
library(lubridate)
library(stringr)
#barack <- read_csv("Data/tweets_potus.csv") 
barack <- read_csv("https://proback.github.io/264_fall_2024/Data/tweets_potus.csv")
#michelle <- read_csv("Data/tweets_flotus.csv") 
michelle <- read_csv("https://proback.github.io/264_fall_2024/Data/tweets_flotus.csv")

tweets <- bind_rows(barack |>
                      mutate(person = "Barack"),
                    michelle |>
                      mutate(person = "Michelle")) |>
  mutate(timestamp = ymd_hms(timestamp))

```

```{r}
barack_tweet_count <- nrow(barack)
michelle_tweet_count <- nrow(michelle)
tweet_counts <- data.frame(
  person = c("Barack", "Michelle"),
  count = c(barack_tweet_count, michelle_tweet_count)
)
ggplot(tweet_counts, aes(x = person, y = count, fill = person)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Total Number of Tweets by Barack and Michelle Obama",
       x = "Person",
       y = "Tweet Count")
```

According to the plot, Michelle Obama had much more tweets than Barack Obama. 

1. How many @ did Barack Obama used in his text, and how many @ did Michelle used in her tweets.
```{r}
barack_at_count <- sum(str_count(barack$text, "@"))
michelle_at_count <- sum(str_count(michelle$text, "@"))
barack_at_count
michelle_at_count

```
It seems like Barack Obama used 94 @ in his tweets, and Michelle used 4172 @ in her tweets.



```{r}

barack_avg_length <- mean(nchar(barack$text[str_detect(barack$text, "@")]))
michelle_avg_length <- mean(nchar(michelle$text[str_detect(michelle$text, "@")]))
barack_avg_length
michelle_avg_length
```

In their tweets that including special character @, the average length of Barack Obama's tweets is 128.631 words, and the average length of Michelle Obama's tweets is 132,1958 words.

```{r}
barack_counts <- data.frame(
  string = c("@", "#", "RT", "-mo"),
  count = c(
    sum(str_count(barack$text, "@")),
    sum(str_count(barack$text, "#")),
    sum(str_count(barack$text, "\\bRT\\b")), 
    sum(str_count(barack$text, "-mo")) 
  )
)
ggplot(barack_counts, aes(x = string, y = count, fill = string)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Special String Counts in Barack Obama's Tweets",
       x = "String",
       y = "Count") 
```

```{r}
michelle_counts <- data.frame(
  string = c("@", "#", "RT", "-bo"),
  count = c(
    sum(str_count(michelle$text, "@")),
    sum(str_count(michelle$text, "#")),
    sum(str_count(michelle$text, "\\bRT\\b")), 
    sum(str_count(michelle$text, "-bo")) 
  )
)
ggplot(michelle_counts, aes(x = string, y = count, fill = string)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Special String Counts in Michelle Obama's Tweets",
       x = "String",
       y = "Count")
```

It seems like Barack Obama used 94 @, 51#, 17 RT and 0 -mo in his tweets. Michelle Obama used 4172 @, 3532#, 1308 RT, and 7 -bo in her tweets. 

```{r}
barack$Date <- as.Date(barack$timestamp)
michelle$Date <- as.Date(michelle$timestamp)
daily_tweets_barack <- barack %>% group_by(Date) %>% summarize(Count = n())
daily_tweets_michelle <- michelle %>% group_by(Date) %>% summarize(Count = n())
ggplot() +
  geom_line(data = daily_tweets_barack, aes(x = Date, y = Count, colour = "Barack"), size = 1) +
  geom_line(data = daily_tweets_michelle, aes(x = Date, y = Count, colour = "Michelle"), size = 1) +
  labs(title = "Daily Tweet Volume",
       x = "Date",
       y = "Tweet Count") +
  theme_minimal() +
  scale_color_manual(values = c("Barack" = "blue", "Michelle" = "red"))
```

The plot above shows that the daily tweets that Barack and Michelle sent. From the plot, we can see that Michelle Obama sent more daily tweets than Barack Obama, since Barack Obama was the president, so he was busy with his country business. 

```{r}
count_urls <- function(data) {
  sum(str_count(data$text, "http(s)?://\\S+"))
}
barack_url_count <- count_urls(barack)
michelle_url_count <- count_urls(michelle)
print(paste("Barack URL count:", barack_url_count))
print(paste("Michelle URL count:", michelle_url_count))
# Prepare the data for plotting
url_counts <- data.frame(
  Person = c("Barack", "Michelle"),
  URL_Count = c(barack_url_count, michelle_url_count)
)
library(ggplot2)
ggplot(url_counts, aes(x = Person, y = URL_Count, fill = Person)) +
  geom_bar(stat = "identity") +
  labs(title = "Count of Tweets Containing URLs by Barack and Michelle Obama",
       x = "Person",
       y = "Number of Tweets with URLs") +
  theme_minimal()
```

The plot above shows the count of tweets of containing URLs, and Michelle Obama sent more tweets with URLs than Barack Obama.