---
title: "mini-project3"
author: "Peter Gao"
editor_options: 
  chunk_output_type: console
---

```{r}
library(ggplot2)
library(dplyr)
library(readr)
library(lubridate)
library(stringr)
#barack <- read_csv("Data/tweets_potus.csv") 
barack <- read_csv("https://proback.github.io/264_fall_2024/Data/tweets_potus.csv")
#michelle <- read_csv("Data/tweets_flotus.csv") 
michelle <- read_csv("https://proback.github.io/264_fall_2024/Data/tweets_flotus.csv")

tweets <- bind_rows(barack |>
                      mutate(person = "Barack"),
                    michelle |>
                      mutate(person = "Michelle")) |>
  mutate(timestamp = ymd_hms(timestamp))

```

Potential things to investigate:

1. How many @ did Barack Obama used in his text, and how many @ did Michelle used in her tweets.
2. The average length of their tweets where they used @.
3. On which date they both posted tweets.
4. How many @, #, RT (retweet), or -mo (personal tweet from Michelle Obama) did Barack Obama used in his tweets, make a plot.
5. 
```{r}
barack_tweet_count <- nrow(barack)
michelle_tweet_count <- nrow(michelle)
tweet_counts <- data.frame(
  person = c("Barack", "Michelle"),
  count = c(barack_tweet_count, michelle_tweet_count)
)
ggplot(tweet_counts, aes(x = person, y = count, fill = person)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Total Number of Tweets by Barack and Michelle Obama",
       x = "Person",
       y = "Tweet Count")
```

According to the plot, Michelle Obama had much more tweets than Barack Obama. 

1. How many @ did Barack Obama used in his text, and how many @ did Michelle used in her tweets.
```{r}
barack_at_count <- sum(str_count(barack$text, "@"))
michelle_at_count <- sum(str_count(michelle$text, "@"))
barack_at_count
michelle_at_count

```
It seems like Barack Obama used 94 @ in his tweets, and Michelle used 4172 @ in her tweets.



```{r}

barack_avg_length <- mean(nchar(barack$text[str_detect(barack$text, "@")]))
michelle_avg_length <- mean(nchar(michelle$text[str_detect(michelle$text, "@")]))
barack_avg_length
michelle_avg_length
```

In their tweets that including special character @, the average length of Barack Obama's tweets is 128.631 words, and the average length of Michelle Obama's tweets is 132,1958 words.

```{r}
barack_counts <- data.frame(
  string = c("@", "#", "RT", "-mo"),
  count = c(
    sum(str_count(barack$text, "@")),
    sum(str_count(barack$text, "#")),
    sum(str_count(barack$text, "\\bRT\\b")), 
    sum(str_count(barack$text, "-mo")) 
  )
)
ggplot(barack_counts, aes(x = string, y = count, fill = string)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Special String Counts in Barack Obama's Tweets",
       x = "String",
       y = "Count") 
```

```{r}
michelle_counts <- data.frame(
  string = c("@", "#", "RT", "-bo"),
  count = c(
    sum(str_count(michelle$text, "@")),
    sum(str_count(michelle$text, "#")),
    sum(str_count(michelle$text, "\\bRT\\b")), 
    sum(str_count(michelle$text, "-bo")) 
  )
)
ggplot(michelle_counts, aes(x = string, y = count, fill = string)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Special String Counts in Michelle Obama's Tweets",
       x = "String",
       y = "Count")
```

It seems like Barack Obama used 94 @, 51#, 17 RT and 0 -mo in his tweets. Michelle Obama used 4172 @, 3532#, 1308 RT, and 7 -bo in her tweets. 